\chapter{Chapter \thechapter}

\lettrine[lraise=0.1, nindent=0.1em, slope=-.5em]{M}{ikhail} followed the nurse dreamily. He barely registered where they were going. From the corner of his eye, he felt his neurons fire up. It was \textit{her}. Walking towards him, headed the other way. His mouth worked before his brain did:

“Hey!”

She stopped and looked at Mikhail. Her eyes told she didn’t recognize him.

“Oh yeah — hey”, she said, showing a gratuitous smile.

“I said I didn’t want to give money — don’t have much to give to be honest. But that I’d volunteer instead and … here I am!”

“Oh yes!” Her eyes picked up a glimmer of recollection. “Now I remember you! That’s so great and lovely to see you’ve come — you were here to see the kids?”

“Yes I just started.” Mikhail laughed a little. “We played Sonic the Hedgehog with Timmy who really was a nice kid. Didn’t mind it at all.”

“That’s so nice! They love to see new faces around — it can be a bit lonely at times here.”

“Yes I bet. Just here waiting for... I don’t know. Must be lonely. Especially for a kid.”

She smiled. Mikhail felt his brain tensed, searching for clues and answers. Something was slipping away from him. He felt the need to grasp it but at the same time, a part of him felt a satisfying comfort in that happening.

“You are working at the children’s department?”

“No, I am here as part of my studies at the university, I am at the general clinic now, doing my training to become a doctor.”

“Oh wow.” Mikhail’s soul left his body. “That’s. Wow. Great. Not much I can say about that.”

“It’s a lot of work at times and still have a long way to go.” She said smilingly. “But hopefully I’ll get my licentiate degree soon so I can start working on my doctorate. Then I can \textit{finally} start on my specialization. Would love to of course choose pediatrics but there’s only so many places to go around.”

“Uh huh, really cool.”

“It can be pretty tough at times but working with the children helps!”

“Yeah!” He muffled a strong urge to shout.

“But I have to keep going now, you as well seem headed out. It was nice to meet you..?”

“Mikhail”, he said and extended his hand. He felt the soft and delicate touch of her skin.

“Anna. Hope to see you again here.”

She then kept going. Mikhail turned towards the nurse who expectantly stood waiting for them to finish. He followed her along. His body felt ethereal and light as a feather. He was floating in the air, empty of thoughts and ambitions.

He came to the main doors and marched out.
