\chapter{Chapter \thechapter}

\lettrine[lraise=0.1, nindent=0.1em, slope=-.5em]{M}{ikhail} stared at the bus window all the way back home. He didn’t know what to think or feel but he felt peaceful. Tranquil. Part of something for a moment.

The week went by in a hazy blur as Mikhail kept to his old, and new, routines. Cleaning and gaming. Silent anxiety grew inside him like a balloon as Friday drew closer. He ruminated on all the possible ways things could go wrong yet there was a tinge of hope, a chance to meet \textit{her}. 

It was happening. He took the bus to the hospital. An elderly nurse came to see him. A sudden panic rose in his chest.

\textit{What the hell do I have in common with these children? These little amebas, probably all out of their minds from the medication. Hey, what’s up? So you have cancer, huh. Wanna play? }

“This way Mr.Borowitz” The nurse showed the way to the children's recreational area. 

\textit{But at least they won’t live long enough to suffer the trials of puberty. Can’t be bullied if you are dead.}

“It’s great to see young men such as you willing to help children. Anything you enjoy doing that could be shared with the kids?”

“Ehhh, I do play video games a lot.” Mikhail said hesitatingly. 

“Oh that’s wonderful! You know what, there’s an old video game console we have been donated. Timmy loves to play it but sometimes he doesn’t have anyone to play with. He is in the cancer-ward and it would mean the world to him if he could share the games with someone.”

“Okay, I think I can do that”, Mikhail said as they walked into the recreational area. In the corner, there was a big television screen with a feeble and pale kid crouching in front of it, squeezing a controller in his hands. He was staring at it intently.

“Hello Timmy, how are you!”

“Hi”, the child responded.

“We have a visitor here who would want to play with you. Say hi to Mr. Borowitz.”

“Hi Mr. Borowitz.”

Mikhail was flabbergasted by the child’s cool tone. Seemed the child was past beyond the mortal world already.

“Hi Timmy. So... what you are playing?”

“Sonic.”

“Sonic the Hedgehog? I know that game.” Mikhail recollected the long hours he had spent running through those golden circles.

“I can’t get past Robotnik...”

“Oh? Well, maybe I can help.” Mikhail walked to the child and gently nudged off the controller from his tiny hands. “I’ll set up the two-player mode so I can take Tails.”

\textit{Goddamn, it’s been a while since I saw a Sega Mega Drive. This could be fun. }

Mikhail felt the old console stir wisps of nostalgic magic, flying through his barren soul. How it was when he played as a child. Honest fun, without constant competition against others. While it had been a while since he had last played, Mikhail’s fingers quickly recollected the long-practiced muscle motions. 

Timmy’s Sonic ran around like a buffoon while he, as Tails, carried him through the game. Mikhail didn’t mind his silly mistakes though. Not even when they lost the level because of it and had to start again.

“Wow, we made it through!” Timmy’s eyes gleamed excited. Mikhail let out a hearty laugh.

“Nice job Timmy.” He said and held out his hand for a high-five. He could barely feel Timmy’s small and frail hand touch his. “We make a good team.”

“No one else wants to play with me”, Timmy coughed. “I’m glad you did.”

“It’s okay, that’s why I came here.” Mikhail cringed internally.

“Timmy”, the nurse — who had come again after having let them play — spoke gently. “It’s time for your medicine.”

“I have to go.”

“Sure. Maybe we can play some another time.” \textit{If you are not dead.}

“Yeah!” Timmy’s eyes glimmered.

Mikhail stared at the TV screen, his mind blank. He realized that he had not seen \textit{her} the whole time. A tinge of sadness washed over him.

\textit{What the fuck am I doing here? Fucking idiot. There’s no chance she even works here. Just wanted to make sure a dummy like me would be lured into wasting their time, amusing these dying retard children.}

Mikhail took a deep breath.

\textit{Well, lesson learnt. Probably she won’t come but hell, if she did. She should be impressed with me sticking with these children. }

“Mr. Borowitz, it’s past seven now so there’s no need to stay.”

“Oh, okay yeah.”
