% \lettrine{}{} command typesets a drop cap in the document
% second brace set formats text placed inside as small caps
% (same thing as doing \lettrine{L}\textsc{orem ipsum ...}

\cleardoublepage % Make sure contents page starts on right-side page

\chapter{Chapter \thechapter}

\lettrine[lraise=0.1, nindent=0.1em, slope=-.5em]{S}{un} kept shining bright into Mikhail’s eyes. His morning slumber was constantly harassed by these photons, beamed by a cosmic entity of scale his ape brains could barely comprehend. He didn’t care though. He tried to close the blinds but they had been broken since the day he moved in. \textit{Fuck this}, he thought to himself. Another day ruined.

He walked into his small kitchen that was almost adjacent to his untidy bed. Small benefits of living in a studio apartment. The coffee was stale, he hadn’t emptied it yesterday. Why bother? Didn’t alter the taste.

Scooping up coffee grinds from a cheap, monocolored bag he steadily filled the drip machine to full. For him, the taste was gratuitous. The only thing that mattered was the quantity.

Setting the machine to bubble its procedure, he sat down and stared into the outside from his window. It was quite awkward to do since the glass was smutty from all the dirt which had slowly accrued over the years without maintenance.

There it was, the world. With its tempting bright sunshine and soft clouds, floating above the green shrubbery. His eyes kept their gaze yet not a single inspiring thought came to his mind, to seduce him to venture into it. It was somewhat paradoxical since yesterday he \textit{definitely} felt he could use some outside. But now, given the comfort of his kitchen with its coffee machine dripping, it seemed relatively complicated and difficult. Maybe he would rather just stay in.

As the caffeine shot through his veins the reality finally seemed to come coherent. \textit{Fuck I should clean up these cans and these filthy clothes. Take out the trash before it rots. Fuuuck!}

Having his mind finally evoked, it found a familiar trail instead that seemed more inviting. \textit{Or maybe…}

He quickly rose up, the coffee cup in his hand and almost jumped to his lousy coach. The PlayStation controller was still blinking being charged full from yesterday, and he immediately turned it on.

\textit{Fucking noobs I am going to wreck you today.} He smiled wryly.

Entering the lobby, there was a tingling sensation over his body. Like it knew a day of epic victory was ahead. Conquest for the ages, saga equal to that of the warriors of the past. He had become so virtuous in the game that many barely could even react before he had smoked them. And we are talking about the best of the best. His skill was just other-worldly.

Mikhail’s mind and body worked as one, flawlessly executing maneuvers as if he could almost anticipate the enemy’s response.

“Fucking noobs”, he thrashed to the headset. “Git gud and learn to play!”

The virtual world kept Mikhail entranced as the game demanded all of his focus, leaving no room for distressing thoughts about his current situation. His immediate chaotic and messy surroundings, lack of human contact — not to even mention intimacy. How he had ended up living in this miserable suburb, locked away from any chance for social interaction.

“Back to the lobby boys!”

The brief hiatuses between games left a narrow opening for boredom and intrusive thoughts which compelled him to make a change. 

\textit{Maybe I should contact Peter over Discord. Ask how he's doing.}

He started sifting through the games.

\textit{But why bother, he is probably busy with his wife and the young kid. It’s never too late to abort, I always tell him. We’ll never again share those weekend-long gaming sessions together.}

A new game started. Mikhail’s attention was immediately drawn to the game loop as he found innovative ways to humiliate his opponents. He chuckled out loud while performing a degrading team wipe all by himself. And then a classic t-bag in the end.

\textit{It never gets old! }

A murmuring sensation in his stomach reminded him that he was still a human, and needed to fill those pesky anatomical needs. He got up, begrudgingly, slouched to the fridge, and a bright white light illuminated the room. It was already getting dark outside. The only thing in the fridge was an empty ketchup bottle.

\textit{God dammit. No way I’m going to the store and cook today. Waste of time and energy.}

He opened up an app from his phone to order the same meal he always did from a Thai place — panang curry. \textit{Why risk getting something bad}, he thought. Mikhail pushed the pile of old takeaway boxes to a corner of his kitchen table. There was no need to clean them up yet.

\begin{center}
\textbf{DING DING}
\end{center}

The food had arrived. Mikhail waited for the delivery woman to leave so there would be no social interaction, no exchange of meaningless pleasantries. He put on a stream from Twitch where a renowned legendary player was playing the same game as he did, and munched the sustenance without noticing its taste, his attention fixed to the screen. He picked up a few new tricks from the master, and booted up his PlayStation.

\textit{Time for dessert! I’ll stomp these scrubs with spicy ways to burn them alive. }

Mikhail preferred the night. It was quiet in the building and outside. No children screaming, couples fighting or other sounds of life disturbing his bubble. There was only him and the game.

The night went near perfect. He lost only a couple of games here and there, to elite players like himself. He was nearing the top 10 in the worldwide leaderboard, a long-time goal of his.

People started their cars, and made noise in the hallway as they hurried to work in the morning. Mikhail looked down on the sheep, feeding the corporate machine for crumbs. He had solved the money problem by figuring out what benefits he could get and what papers to send every month. Also he had inherited all his mother’s money when she died a year ago. 

He suddenly felt tired, his fingers fumbling his character to a lousy death. The exhaustion of the battle had finally settled in and Mikhail collapsed on the bed, feeling quite satisfied with his conquests. He fell into slumber without dreams.
