\chapter{Chapter \thechapter}

\begin{center}
\textbf{DING DING}
\end{center}

\lettrine[lraise=0.1, nindent=0.1em, slope=-.5em]{M}{ikhail} stirred. He was lying across his bed in an untidy mess of greasy linen and old crumbles of food. Barely conscious, his brain tried to spark a modicum of connections but in vain.

\begin{center}
\textbf{DING DING}
\end{center}

\textit{Who the fuck is at the door...}

Mikhail quickly put on his filthy pants, stumbling as he walked to the front door. He pushed down the handle.

“Hello”, said a soft feminine voice. “May I interest you in participating in the yearly fundraising for sick children?”

“What”, Mikhail said, still rubbing his eyes.

“Oh, I’m sorry — did I wake you? It wasn’t my intention.” It finally penetrated his dull mind what he was seeing. A young woman, couldn’t be over 30, was standing at his door. Clothed in a smart but casual jacket, wearing no hat to cover her long flowing blonde hair. Her two blue eyes gazed at him, quizzingly.

“Ah yeah, no problem. Just a little sleepy in the mornings.” Mikhail laughed dryly. 

She gave a short laugh as well. “Apparently.” She did not seem overly appalled by the obvious decadence and filth standing before her. “I was just asking if you were interested in participating in a fundraising for sick children.”

“Oh, okay. Yeah, well. I haven’t participated much in those”, Mikhail mumbled.

“It’s fine to start now”, she answered, her pearly white teeth gleaming.

“Uhh, yeah. I mean. Aah.” Mikhail’s brain searched for a snide response. It was on his tongue but he just did not dare to say it. Did not dare to break the mirage.

\textit{Fucking bitch}, it suddenly hit him. \textit{Trying to fool me into giving my money away.}

“I don’t really care that much.” 

There was a moment of pause. Her gaze was steady but a crack had come visible. Whatever illusion she had of him, had disappeared. He was filth, both in body and soul.

“Oh, I see. Well then, have a nice day.”

She waved and turned to leave. Mikhail instinctively went to close the door.

“But if, you know, there were other ways to help than money”, he blurted. “I might…”

The girl turned back.

“They actually do take in volunteers who can spare time to be with the children at New Port. If you are interested, there’s a form on the website you can fill and ask!” She smiled.

“Yeah, okay.” Mikhail answered. “Thanks. Bye.” He shut the door.

“Bye!” she replied in a chirpy tone.

\textit{What the fuck was that. That was so fucking pathetic. Fuuuck!}

He smelled his armpits. They smelled appalling. Feeling a surge of energy, he rushed to the bathroom and started showering, vigorously scrubbing his hair. Taking a good look at his unshaven face, he scrounged his cabinet for a trimmer and started taking big chunks off from his ungodly tangle of a beard.

Mikhail gazed in the mirror. The person who stared back looked like a stranger. Long, partly matted hair was tied in a neat bun. The woodsman beard suited him, stylish yet sufficiently scruffy. Fresh mint odor rose beneath his clean black t-shirt. He stared at the reflection perplexed, thinking about what the hell just happened.

\textit{My stupid genetic code, realizing itself via a banal grooming ritual for a slim chance to pass my second-grade genetic material into the future.} She was hot though. \textit{No, what the fuck am I doing? Am I going outside? For what? For a faint hope to meet her again and to seduce her? How? Like in movies, just walk to her and say I think you’re pretty?}

A distant memory surged from a dark corner of Mikhail’s mind, something he had buried a long time ago, given up on. It was him holding hands with her best friend Alexandra, they were teenagers then. They kissed, and fell asleep in a hammock. 

Shortness of breath, and throbbing pain in his chest stopped recalling the memory. 

\textit{Do I want to take that leap of faith again? To open myself just to have my heart stabbed repeatedly with shards of glass? There are games to be had, and noobs to be dominated. This is the safe way, this is what I can control, what I deserve. Happiness is anyway fleeting as the dopamine and oxytocin evaporates from my system, what remains is only heightened suffering after the high. I prefer my woes constant and ever-flowing.}

Mikhail started to clean his apartment, perhaps for the first time in years. He did not know how. It was akin to a trance, his hands did the work but his mind was absent. There was a strange sparkly sensation within him, something he had forgotten was possible. The lights outside were a little brighter, his appearance suitable, even appealing to others. Existence did not seem like such a terrible deal after all.

Was this hope? \textit{I don’t want hope, hope is killing me! How can I get rid of this feeling?}

The day was done and he came to a sudden realization he had not booted up his PlayStation today. The studio was neat and clean and he was tired. His soul felt cleansed as did the filthy countertops. Yet still, his mind compelled him to open up his dusty computer, to search “New Port hospital”. He found the sick children section, all of them looking so anemic and disabled. A link titled “Volunteer work” described a recurring call for volunteers every Monday afternoon at the hospital.

\textit{Would she be there? But I despise children! When was the last time I had been out?} It felt to him like years, besides running the bare minimum errands, to have properly done something out of his own will. Her golden hair and smile were stuck in his mind in a perpetual loop. \textit{Have I finally lost it?} He had feared this day might come. 

Mikhail felt exhausted, his body not being used to such physical exercise as cleaning the studio required. His mind was drained as well, the new stimulus and call for an adventure had taken him on a rollercoaster ride to the past, and even worse, to the present. To the realization of what he lacked. What he thought he could live without. Mikhail stared at the roof, and fell asleep quickly, not able to resolve what he would do the next day.