\chapter{Chapter \thechapter}

\lettrine[lraise=0.1, nindent=0.1em, slope=-.5em]{H}{aving} found an actual goal in his life, Mikhail felt uncomfortable. Uncomfortable by the burden of the task that he had brought upon himself. His interest in playing decreased every day as the moment of truth came closer. The normal dishes he ordered from the Thai place appalled him. He ordered a salad for the first time in his life. It tasted good. New. Weird.

He took upon a new hobby to keep his beard and the house tidy. Every morning he would check whether there was something to do. A stray hair here. A coffee stain on the table there.

Mikhail also felt a sudden interest in learning about children. A subject he thought he’d never dwell into but there he was, finishing Wikipedia page after another about their conditions. The psychological and biological problem. Most fatal diseases. Diseases that most likely disabled them. Stuff like that.

Laying on his bed, Mikhail daydreamed about how the day would go when he finally arrived at the hospital. What he would say to the doctors or nurses. How he would greet the kids. What he would do if he met \textit{her}.

Her. He didn’t even know her name. Mary. Rose. Emily. Something sweet like that.

Her face also became mistier in his mind. Were her eyes blue or green? What was her face like? Her voice — how did her voice sound like?

Mikhail conjured up the details as he dreamt and felt somewhat sure that they would eventually meet again. He wasn’t spiritual at all but it felt, somehow, ordained to him. A destiny of kinds.

While staring at his sluggish and unmuscular image, he felt a physical need to move. His muscles were as soft as a baby's butt. No woman would be charmed by that.

So Mikhail started to do push-ups in the mornings. Or more like tried to do. The mechanics still eluded his body and his arms quickly came to exhaustion. He needed to be better. Just being funny wouldn’t be enough.

But he counted on that though. That it was his brains, if anything, that would eventually convince her to give him a chance. \textit{Everybody loves a guy who makes them laugh.} Or so Mikhail had read. It seemed that they both shared a similar affection for self-deprecation. It would be Mikhail’s strongest asset.

Switching between his dreams and reality seemed to get harder and harder when Monday was upon him. Mikhail woke up sharply in the early morning and couldn’t get back to sleep. The weight of the moment became heavier and heavier as the clock raced towards 5:30 PM. He felt again disappointed in himself and apathetic. Whatever delusions he had were again washed away by endless self-pity and hatred. \textit{What the fuck am I doing…}

4:30 he got to the door. The handle felt heavy in his hand. He walked to the bus stop and triple-checked the number he should take and whether if that would fail to arrive, what his second option would be.

The bus came. Everything seemed to be in place. It was his destiny.

Walking to the hospital Mikhail checked his phone. It was 5:12. He had arrived plenty early. An unusual feat for him, for certain. Mikhail started to feel again anxious as he stepped on the hospital stairs. 

He walked to the counter.

“You take a left turn from there”, the receptionist replied sharply. And you look for room D112 in the corridor — there should be a person to meet with you.”

“Thanks”, Mikhail said and walked. He felt out of place in the sterile environment of the hospital. Where everyone seemed to have a clear purpose.

He slumbered to an open door from where a nurse beckoned him to come in.

Walking in he saw 5 people sitting on chairs, 4 middle-aged ladies and one middle-aged man. Seemingly middle-class with probably golden retrievers and proper jobs.

“Please, take a seat” the nurse said.

“Glad to see young people here as well”, she spoke sweetly as he sat down. Mikhail felt their glances.

Few people came after him. Nurse checked her list and after a while, went to close the door. “So. Now I want to get to know you all a little bit and what are your goals with the volunteer work. Let’s start from the first of the list — Lisa Bigsby.”

One of the middle-aged ladies stirred. “Oh, hello — I am Lisa. My niece recently came to the hospital and I’ve been thinking of surprising her by coming here — Anastacia Rowen.”

“Anastacia! Oh right, you are her aunt. She is such a lovely girl, I am sure she’ll be so happy to meet you.”

Mikhail felt a knot turning in his stomach.

“So about the work, we have play hours during the evenings — depending on your schedules. After dinner, we do things like finger-painting or games with the other tenants. Some like to watch TV or play games on their own but we have plenty of children who enjoy spending time with the volunteers.”

Everyone nodded agreeingly. Except Mikhail.

“Next we have Mikhail Borowitz.” All eyes turned towards Mikhail who felt his throat dry shut.

“Hi”, his voice was oddly shrill. “I uhh, am Mikhail. And I…” his voice trailed off.

“So there was this woman who came to me or I mean, knocked at my door. And asked or said she was, from the hospital. And they were looking for volunteers or something. And I said I would. Be interested in.”

He looked at the nurse’s eyes, still staring at him. His stomach slowly seemed to set.

“And so I came to see if I can help.”

“You have no relatives here?” the nurse asked.

“No, I don’t think so.” \textit{They are all luckily dead.}

“You just came out of the blue here?” She sounded somewhat amazed. “Anybody else here who does not know anyone at the hospital?”

No hands were raised. 

“Well then, that’s very brave of you, Mikhail. We don’t often get people who come here just like that. So, as I said, we have after hours from 5 PM forward when the children are available for play — depending on your schedule. Does that sound good?”

“Sure.”

“Any particular time you have in mind, people often come here once a week. Days like Wednesday are quite crowded but I’m sure we can fit you all in.”

“Uhh, any day really is fine”, Mikhail mumbled.

“Maybe Friday?”

“Okay.”

“From 5 or later? We are open till 7 but it’d be best to come early — some kids don’t like late visitors. And we have the medication at 8 so that takes time to prepare.”

“Yeah well, maybe 5:30 would be good.”

“Okay, I set you for 5:30. Now, who is Georgia Richards?”
