\chapter{Chapter \thechapter}

\lettrine[lraise=0.1, nindent=0.1em, slope=-.5em]{T}{he} next day, the Sun did not shine. Mikhail woke up to the quiet tapping of rain on his window. The outside was misty and gloomy. He gathered up the strength to go to his coffee maker.

Sipping his third cup and staring at the cleaned apartment, the mania that had taken hold of him seemed to dissipate. There was \underline{no chance} he would see that girl at the hospital. Not a chance in a million. And if by chance he \textit{would} see her, what was he going to say? Hi? \textit{Yeah I hate children but I like you so, it balances out ha ha?}

He already felt a wave of humiliation washing over him. That was the last thing he needed. Just being ridiculed once more for being an ugly motherfucker. Better for him to stay in his cave.

Bombarded by these thoughts the fantasy of saving his soul from oblivion seemed to vanish as quickly as it had come. \textit{And why even bother? It’s all meaningless anyway. And the hospital is like 30 minutes away. And what the fuck would I even do there, just play games with some retarded child? Fuck that…}

\textit{And it’s raining, great!}

He sat on the couch and booted up the PlayStation. The familiar logos created a sense of security. In the history of mankind there had been moments when against the great unknown, an individual took a great leap with dauntless courage. This was not one of those moments.

The familiar trance of virtual reality engulfed Mikhail and all the worries in the world were washed by its wake. The rejuvenating sensation of victory — unmatched superiority — gave him his much-needed dopamine.

Hours passed. The rain kept dribbling and Mikhail, while beating yet another unimaginable odds, felt hungry and ordered a pizza. He ate. His body numbly followed its daily routine. Glancing at the couch where the inevitable chaos was already settling in, his mind wandered and the room seemed smaller. Lonelier. Darker.

He stared at his window, imagining prison bars instead of blinds. A wave of melancholy washed over him. From the deep recesses of his mind, a string of tortuous thoughts arrived like hyenas, feeding on his despair. The fog of the trance he had been in was lifted and he saw the desolation of his being in full. Alone in a lousy studio apartment. With no job. Living from government welfare. The cleanliness made the absence of it all even more visible. Just an empty shell of human existence.

\textit{How can I live in this rat hole when there’s a world full of love and excitement just outside?}

The thought pierced his soul. The lashes of self-pity, how hard they fell on his dull mind. He finished his pizza. The mechanics of moving around stirred his body away from the hole it had sunken into.

\textit{Why was I even born? To suffer like this. A fucking joke.} He asked himself repeatedly. He threw the pizza box into the trash with rage.

He sat on the couch trying to continue playing. He felt nothing. His only joy had been taken away from him. He hesitantly turned off the PlayStation. The room was empty and alone. He reached for his phone. He knew some people although he wouldn’t call them friends. Just a bunch of weirdos like him. He checked his messages. Nothing.

He stared at the screen, trying to figure out what to type. “Hey, wanna hang out?” Ugh. \textit{That sounded so fucking lame.} He settled after a good half an hour for a line: “Yo, what’s up? Wanna grab a beer?” He pressed send.

Having completed this almost insurmountable task he felt exhausted but also relieved. \textit{Okay, I suck but at least there are others like me. So it’s not that bad. I guess.} He felt a small tingle of purpose in his existence. Fiddling around on the couch trying to figure out what else to do, he again turned on the PlayStation. He kept playing until the early morning.