\chapter{Chapter \thechapter}

\lettrine[lraise=0.1, nindent=0.1em, slope=-.5em]{T}{he} studio was hot when Mikhail woke up and the first thing he did was check his phone. A new message in WhatsApp. From an acquaintance, a fellow loser like himself, who had replied at 04:32 AM. He agreed to meet in the evening for a beer in a local dingy bar. \textit{Misery is best shared}, Mikhail thought and agreed to the offer.

Maybe he could bounce ideas with the guy on what to do with his situation, not that the dude had any experience in relationships. He saw he had received an email recently. He opened it. It was a short notice that thanked him for his application and that they were looking forward to seeing him on Monday.

\textit{What the fuck?}

Mikhail apparently during his mania had, by accident, sent his half-finished application. His breath shortened and stopped for a while. His mind was racing. He saw all the possible ways the social interactions would go wrong.

\textit{So first I have to figure out how I talk with the nurses without appearing like a maniac. Then I have to talk with the fucking children. What if I end up shouting at them? Or just hitting one? What if they start laughing at me? For being such a loser.}

And if she would be there, seeing all this. Toiling around like an idiot with no idea how to interact with the kids. \textit{Shit.}

\textit{Or maybe I just don’t go.}

He checked the time. \textit{At least I’ll meet Joey in a couple of hours. Maybe we’ll figure out something.}

Feeling a need to be distracted, Mikhail set up an alarm and booted up the PlayStation. He wanted to wash away all the negative thoughts by falling into the flow of playing.

His alarm blared, bringing him to the present.

He put some clothes on and headed out. Mikhail enjoyed the sensation of the cool night breeze. The soothing absence of crowds, only creatures of the night like himself.

Finding his way to the local hub of pubs, he saw the ugly faces of the regulars. Drunk and talking about bullshit as usual. Some ladies smoking by the corner of the bar, lost in lively banter. A single female exhaling a long billow of smoke while staring silently at him. All fooling themselves by the shared aimlessness.

Mikhail ordered a pint from the counter and saw Joey with a side glance. Sitting in a cozy dim corner, sipping beer. He seemed shocked when he realized that it was Mikhail who was walking towards him.

“Wow dude! What the hell happened to you?” He chuckled. “Are you having a date tonight?” 

Mikhail laughed in turn. “What do you think?” He took a heavy gulp from his beer, its stale taste feeling rather homely.

“I don’t know really. It’s been so long since we last met, you could have hit up some old lady from the laundry.”

“Naa. Just felt like cleaning up my apartment.”

Joey seemed in disbelief.

“Okay, jeezs.”

A grin appeared on Mikhail’s face.

“Well there was this girl that knocked on my door.”

“Fucking knew it!” Joey shouted.

“She was trying to get me to donate money to the children’s fucking hospital, can you believe it?”

They both laughed.

“What the hell she was thinking? You like, hate children. And every time we meet you end up blabbering about how humans are the worst and there should be an apocalypse to kill everyone. That the whole world is mad and we should finish it sooner than later.”

“Yeah...”

“But seriously — did a body snatcher get you or what? You look like Mikhail’s brother or something.”

Mikhail smirked a little.

“I don’t know man. It’s so hard to explain. She was just too… nice. Like she didn’t seem to care I looked like a homeless guy. And fuck, the worst part of it is — I promised to go the hospital.” Mikhail laughed heartily.

“What?”

“Yeah, so she was asking for money for those sick children or whatever. And I said, the cheap bastard I was, that no way. But because she was just too nice I somehow promised I could help them in person, in the hospital. And that’s when I kinda went crazy because I don’t know what the hell I'm doing right now.”

“Wow, dude. Really?”

“Yeah, it’s weird. The chances of meeting her are probably zero but I don’t know if this is worth a shot. To see those brain-damaged children and play hide and seek or something.”

They both laughed and started an honest discussion about what to do. Mikhail felt somehow connected to the world which was strangely compelling. Jointly their inept social experience almost made up what a normal person would know automatically. The intoxication washed away most of the hindrances of inhibition and as the clock hit last call, Joey pulled him close.

“Dude just fucking do it man. Go there and pretend you are interested in the kids while you see if the hotty is still there. If not — just bail but you never know if she’s crazy...”

“Yeah yeah”, Mikhail nodded. Agreeing in a drunken stupor. “What’s the worst that could happen?”
